```{r include=FALSE}
library(easypackages)
libraries('tidyverse','lubridate','janitor','showtext',
          'summarytools','tidymodels')
theme_set(theme_light())
font_add_google('Roboto Slab','Roboto Slab')
showtext_auto()
tidymodels_prefer()
options(scipen=999)
```

### Read titanic dataset

#### Data Dictionary 

+----------------------+---------------------------------------------+---------------------------+
| Variable             | Definition                                  | Key                       |
+======================+=============================================+===========================+
| survival             | Survival                                    | 0 = No, 1 = Yes           |
+----------------------+---------------------------------------------+---------------------------+
| pclass               | Ticket class                                | 1 = 1st, 2 = 2nd, 3 = 3rd |
+----------------------+---------------------------------------------+---------------------------+
| sex                  | Sex                                         |                           |
+----------------------+---------------------------------------------+---------------------------+
| Age                  | Age in years                                |                           |
+----------------------+---------------------------------------------+---------------------------+
| sibsp                | \# of siblings / spouses aboard the Titanic |                           |
+----------------------+---------------------------------------------+---------------------------+
| parch                | \# of parents / children aboard the Titanic |                           |
+----------------------+---------------------------------------------+---------------------------+
| ticket               | Ticket number                               |                           |
+----------------------+---------------------------------------------+---------------------------+
| fare                 | Passenger fare                              |                           |
+----------------------+---------------------------------------------+---------------------------+
| cabin                | Cabin number                                |                           |
+----------------------+---------------------------------------------+---------------------------+
| embarked             | Port of Embarkation                         |                           |
+----------------------+---------------------------------------------+---------------------------+

```{r}
titanic <-
  read_csv('https://gist.githubusercontent.com/michhar/2dfd2de0d4f8727f873422c5d959fff5/raw/fa71405126017e6a37bea592440b4bee94bf7b9e/titanic.csv') %>% 
  clean_names()


titanic <-
  titanic %>% 
  mutate(embarked = case_when(
    embarked == 'C' ~'Cherbourg',
    embarked == 'Q' ~'Queenstown',
    embarked == 'S' ~'Southampton'
  )) %>% 
  mutate(across(where(is.character),factor)) %>% 
  mutate(survived = factor(survived)) %>% 
  select(-ticket)

titanic %>% 
  map_df(~sum(is.na(.)))

```

### Ordering Steps

\*\* Update role then do following

1.  Impute

2.  Handle factor levels

3.  Individual transformations for skewness and other issues

4.  Discretize (if needed and if you have no other choice)

5.  Create dummy variables

6.  Create interactions

7.  Normalization steps (center, scale, range, etc)

8.  Multivariate transformation (e.g.PCA, spatial sign, etc)

### 1.1 Impute embarked varriable

```{r}
titanic %>% 
  group_by(embarked) %>% 
  summarise(count = n(),
            avg_age = mean(age,na.rm = T),
            avg_fare = mean(fare,na.rm = T))

titanic %>% 
  filter(is.na(embarked))

```

```{r}
# Imputed by mode
titanic %>% 
  recipe(survived ~.,) %>% 
  step_impute_mode(embarked) %>% 
  prep() %>% 
  juice() %>% 
  filter(passenger_id %in% c(62,830))

# Impute by KNN 
titanic %>% 
  recipe(survived ~.,) %>% 
  step_impute_knn(embarked) %>% 
  prep() %>% 
  juice() %>% 
  filter(passenger_id %in% c(62,830))

```

### 1.2 Impute age varriable

```{r}
# Check density of current
titanic %>% 
  ggplot(aes(age)) +
  geom_density()

# 
titanic %>% 
  recipe(survived ~.,) %>% 
  step_impute_median(age) %>% 
  prep() %>% 
  juice() %>% 
  ggplot(aes(age)) +
  geom_density()

```

## 2.1 Individual transformations for skewness and other issues

```{r}
titanic %>% 
  select(where(negate(is.factor)), -passenger_id) %>% 
  gather() %>% 
  ggplot(aes(value, fill = key)) + 
  geom_histogram() + 
  facet_wrap(~key , scales = 'free_x') +
  scale_x_log10()

# Look like fare need to be log10 for not better normal distribution 
titanic %>% 
  recipe(survived ~.,) %>% 
  step_impute_knn(embarked) %>% 
  step_impute_median(age) %>% 
  step_log(fare,base = 10) %>% 
  prep() %>% 
  juice()
  
```

### 5.1 Create dummy varrible and Zero varriance

```{r}
titanic %>% 
  recipe(survived ~.,) %>% 
  update_role(c(passenger_id,name,cabin),new_role = 'ID') %>% 
  step_impute_knn(embarked) %>% 
  step_impute_median(age) %>% 
  step_log(fare,base = 10) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  step_zv(all_predictors()) %>% 
  prep() %>% 
  juice()

```

### 7.1

```{r}
titanic %>% 
  recipe(survived ~.,) %>% 
  update_role(c(passenger_id,name,cabin),new_role = 'ID') %>% 
  step_impute_knn(embarked) %>% 
  step_impute_median(age) %>% 
  step_log(fare,base = 10) %>% 
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
  step_zv(all_predictors()) %>% 
  step_scale(all_numeric_predictors(), -fare) %>% 
  prep() %>% 
  juice()
```

```{r}
titanic_split <- initial_split(titanic,0.75,strata = sib_sp)
titanic_train <- training(titanic_split)
titanic_test <- testing(titanic_split)
```

### Create Recipe

```{r}
titanic_rec <- 
  titanic_train %>% 
    recipe(survived ~.,) %>% 
    update_role(c(passenger_id,name,cabin),new_role = 'ID') %>% 
    step_impute_knn(embarked) %>% 
    step_impute_median(age) %>% 
  #  step_log(fare,base = 10) %>% 
    step_dummy(all_nominal_predictors(), one_hot = TRUE) %>% 
    step_zv(all_predictors()) # %>% 
  # step_scale(all_numeric_predictors(), -fare) 
```

### Model and evaluate

```{r}
kfold <- vfold_cv(titanic_train, 10, strata = sib_sp)

log_rg_mod <-
  logistic_reg() %>% 
  set_engine('glm')  # Logistic regress has problem with log transform

titanic_wf <-
  workflow() %>% 
  add_recipe(titanic_rec) %>% 
  add_model(log_rg_mod)

titanic_tune <-
  tune_grid(titanic_wf,resamples = kfold, grid = 5)

titanic_tune %>% 
  show_best()

```

### Prediction

```{r}
titanic_fit <-last_fit(titanic_wf,titanic_split) 

titanic_fit %>% 
  collect_metrics()

titanic_fit %>% 
  collect_predictions()

```
