
<https://www.tidymodels.org/start/recipes/>

```{r}
library(easypackages)
libraries('tidyverse','lubridate','janitor','showtext',
          'summarytools','tidymodels','nycflights13','vip','nnet')
theme_set(theme_light())
font_add_google('Roboto Slab','Roboto Slab')
showtext_auto()
tidymodels_prefer()
options(scipen=999)
```

Let's use the nycflights13 data to predict whether a plane arrives more than 30 minutes late. This data set contains information on 325,819 flights departing near New York City in 2013

```{r}
flights_df  <- 
    flights %>% 
      inner_join(weather,by = c('origin','time_hour')) %>% 
      mutate(arr_delay  = factor(ifelse(arr_delay >30,'late','ontime')),
             date = date(time_hour)) %>% 
      select(dep_time,flight,origin,dest,air_time,distance,carrier,date,arr_delay,time_hour) %>% 
      #map_df(~sum(is.na(.)))
      na.omit() %>% 
      mutate(across(where(is.character),as.factor)) 
```

## Split data for train/test

```{r}
set.seed(1024)

flights_split <- initial_split(flights_df,prop = 0.8)
flights_train <- training(flights_split) 
flights_test <- testing(flights_split)
```

## CREATE RECIPE AND ROLES

1.  `update_role()` : Keep this variable, but not use them as outcomes or predictors.
2.  `step_date()` : Create date into one more factor , month, dow (day of week), doy (day of year), week, month, decimal
3.  `step_holiday()` : Create a binary variable indicating whether the current date is a holiday or not.
4.  `step_rm()` : remove varriable
5.  `step_dummy` : create dummy varriables
6.  `step_zv` : remove columns from the data when the training set data have a single value, so it is added to the recipe after `step_dummy()`

When the recipe is applied to the training set, a column is made for LEX,HDN because the factor levels come from flight_data (not the training set), but this column will contain all zeros for testing set. so refer to `step_zv`

```{r}
flights_train %>% 
  distinct(dest) %>% 
  anti_join(flights_test)

#> Joining, by = "dest"
#> # A tibble: 1 x 1
#>   dest 
#>   <fct>
#> 1 LEX
```

```{r}
flights_train %>% 
  recipe(arr_delay ~.) %>% 
  update_role(time_hour,new_role = 'ID') %>% 
  step_date(date,features = c('dow','month')) %>% 
  step_holiday(date,holidays = timeDate::listHolidays("US")) %>% 
  step_rm(date) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  prep() %>% 
  bake(new_data = NULL)
  
flights_rec <-
      flights_train %>% 
        recipe(arr_delay ~.) %>% 
        update_role(time_hour,new_role = 'ID') %>% 
        step_date(date,features = c('dow','month')) %>% 
        step_holiday(date,holidays = timeDate::listHolidays("US")) %>% 
        step_rm(date) %>% 
        step_dummy(all_nominal_predictors()) %>% 
        step_zv(all_predictors())

```

## Define Model & Workflow

```{r}
lr_mod <- 
  logistic_reg() %>% 
  set_engine("glm")

lr_wf <-
  workflow() %>% 
  add_recipe(flights_rec) %>% 
  add_model(lr_mod) 

```

## Fit & Predict

```{r}
lr_fit <- fit(lr_wf,flights_train)

lr_fit %>% 
  pull_workflow_fit() %>% 
  tidy()

# Prediction as a class
flights_test %>% 
    bind_cols(predict(lr_fit,flights_test))

#Prediction as prob 
flights_test %>% 
    bind_cols(predict(lr_fit,flights_test,type = 'prob'))
```

# Evaluate Model

```{r}
# Define metric for evaluate 
class_metric <- metric_set(accuracy,precision,yardstick::spec,recall,kap,f_meas)

# Evalutate 
flights_pred <- flights_test %>% 
                   bind_cols(predict(lr_fit,flights_test))
  
flights_pred %>% 
    class_metric(arr_delay,estimate = .pred)

# ROC Curve
flights_roc <- flights_test %>% 
                   bind_cols(predict(lr_fit,flights_test,type = 'prob'))

flights_roc %>% 
  roc_curve(arr_delay,.pred_late) %>% 
  autoplot()

```

------------------------------------------------------------------------

## CASE STUDY : HOTEL BOOKING CANCELLATION AND PRICE PREDICTION 

```{r include=FALSE}
car.price <- 
  read_csv('https://raw.githubusercontent.com/konjanats/dataset/main/carprice_assignment.csv') %>% 
  clean_names()
```


```{r}
# remove reservation status 
car.price_df <-
  car.price %>% 
    select(-car_name) %>% 
    mutate(symboling = case_when(
      symboling == -3 ~ 'Very Risk',
      symboling == -2 ~ 'High Risk',
      symboling == -1 ~ 'Risk',
      symboling == 0 ~ 'Moderate',
      symboling == 1 ~ 'Safe',
      symboling == 2 ~ 'High Safe',
      symboling == 3 ~ 'Very Safe'
    )) %>% 
    mutate(across(where(is.character),factor)) %>% 
    mutate(price = log10(price))

```


```{r}
car.price_df  %>% 
# map_df(~sum(is.na(.)))
 dfSummary(graph.col = F)
```

## Plot for relationship 

```{r}
car.price_df %>% 
  ggplot(aes(price)) + 
  geom_histogram()
```



### DATA SPLITTING & RESAMPLING 

```{r}
set.seed(1024)
car_split <- initial_split(car.price_df,0.8,strata = carbody)
car_train <- training(car_split) 
car_test <- testing(car_split)

#resampling setting 
car_fold <- vfold_cv(car_train,10)
keep_pred <- control_resamples(save_pred = TRUE, save_workflow = TRUE)

```

### Recipe 

```{r}
car_bake <-
  car_train %>% 
    recipe(price ~.,) %>% 
    update_role(car_id,new_role = 'ID') %>% 
    step_log(all_numeric_predictors(),base = 10) %>% 
    step_dummy(all_nominal_predictors()) %>% 
    step_zv(all_predictors()) %>% 
    prep() %>% 
    bake(new_data = NULL) 
    
car_rec <- 
  car_train %>% 
    recipe(price ~.,) %>% 
    update_role(car_id,new_role = 'ID') %>% 
    step_log(all_numeric_predictors(),base = 10) %>% 
    step_dummy(all_nominal_predictors()) %>% 
    step_zv(all_predictors()) 
```

### Mutlple Model & Workflow Resample

```{r}
# Different Model 
mlp_mod <-
  mlp() %>% 
    set_engine("nnet") %>% 
    set_mode("regression")

lm_mod <- 
  linear_reg() %>% 
  set_engine('lm')

# List of Model & Recipe 
preproc <- list(basic = car_rec)
models <- list(nnet = mlp_mod,linear = lm_mod)

# Workflow set 
wf_set <- workflow_set(preproc,models, cross = TRUE)

# Worflow Mapped 
wf_mapped <- 
  wf_set %>% 
    workflow_map('fit_resamples',seed = 1024,verbose = TRUE, 
               resamples = car_fold , control = keep_pred )

# Collect Matrix
collect_metrics(wf_mapped) 

```

## Workflow and Fit 

```{r}
# Workflow 
nnet_wf <-workflow() %>% 
            add_recipe(car_rec) %>% 
            add_model(mlp_mod)

lm_wf <-workflow() %>% 
            add_recipe(car_rec) %>% 
            add_model(lm_mod)
 

# Fit model 
nnet_fit <- fit(nnet_wf,car_train)
lm_fit <- fit(lm_wf,car_train)

nnet_fit %>% 
  pull_workflow_fit()

lm_fit %>% 
  pull_workflow_fit() %>% 
  tidy() %>% 
  arrange(p.value)
```

# Predict & Evaluate 

```{r}
car_test %>% 
  bind_cols(predict(lm_fit,car_test)) %>% 
  bind_cols(predict(nnet_fit,car_test))
  
car_pred <-
  car_test %>% 
    mutate(lm_pred = pull(predict(lm_fit,car_test)),
         nnet_pred = pull(predict(nnet_fit,car_test)))

car_metrics <- metric_set(rmse, rsq, mae)
car_metrics(car_pred, truth = price, estimate = lm_pred)
car_metrics(car_pred, truth = price, estimate = nnet_pred)

```
# Plot Model performace 

```{r}
car_pred %>% 
  ggplot(aes(lm_pred,price)) +
  geom_point() +
  geom_abline(lty = 2) +
  coord_obs_pred() +
  labs(x = 'Price (log10)' ,
       y = 'Price Prediction (log10)')
```

# Varriable Importance

```{r}
lm_fit %>% 
  pull_workflow_fit() %>% 
  vip()
```



